Pottery decor as networks on the Middle Niger

### 2024-06-10 analysis/paper/paper.Rmd
300 dpi picks

---
title: "Pottery decor as networks on the Middle Niger"
author:
  - Nikolas Gestrich:
      email: gestrich@uni-frankfurt.de
      institute: [FI]
      correspondence: true
  - Juan-Marco Puerta-Schardt:
      email: Puerta-Schardt@em.uni-frankfurt.de
      institute: [GU]
      correspondence: false
institute:
  - FI: Frobenius Institute
  - GU: Goethe University
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      #pandoc_args:
      #- --lua-filter=../templates/scholarly-metadata.lua
      #- --lua-filter=../templates/author-info-blocks.lua
      #- --lua-filter=../templates/pagebreak.lua
abstract: |
  This paper reports on an attempt to analyse decorative techniques on archaeological pottery from the Middle Niger as knowledge exchange networks. The 12th-century CE state of this network is modelled and analysed, and then compared to its 9th-century counterpart. The analysis shows how knowledge about pottery decoration was propagated within networks of different sizes and intensities, from local, well-connected networks to more loosely tied long-distance connections. The article shows how the perspective of network analysis differs from, and can fruitfully complement, previous treatments of ceramic décor distribution in the region. It adds a novel perspective to what the distribution of archaeological ceramics in this region reflects, and contributes to the generation of hypotheses that can be further tested by fieldwork. 
keywords: |
  Mali; network analysis; pottery; archaeological ceramics
---

@@

```{r iNext overview, echo = FALSE}
library(iNEXT)

@@

```{r cluster3, fig.cap="Internal connections within community 3"}
decor_graph %>%
  activate(nodes) %>%
  mutate(deg = centrality_eigen(weights = weight)) %>%
  filter(louvain == 3) %>%
  ggraph(layout = "graphopt") +
  geom_edge_fan(aes(color = name, edge_width = weight, edge_alpha = weight)) +
  scale_edge_color_manual(values = decorcolor[E(decor_graph)$name]) +
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_point(aes(size = centrality_degree(weights = weight)), colour = "darkgreen") +
  geom_node_text(aes(label = label), col = "black", repel = TRUE) +
  guides(color = "legend", edge_width = "none", size = "none")+
  theme_graph()
```

```{r cluster4, fig.cap="Internal connections within community 3"}
decor_graph %>%
  activate(nodes) %>%
  mutate(deg = centrality_eigen(weights = weight)) %>%
  filter(louvain == 4) %>%
  ggraph(layout = "graphopt") +
  scale_edge_width(range = c(0.2, 2)) +
  geom_edge_fan(aes(color = name, edge_width = weight, edge_alpha = weight)) +
  scale_edge_color_manual(values = decorcolor[E(decor_graph)$name]) +
  geom_node_point(aes(size = centrality_degree(weights = weight)), colour = "yellow") +
  geom_node_text(aes(label = label), col = "black", repel = TRUE) +
  guides(color = "legend", edge_width = "none", size = "none")+
  theme_graph()
```

>>>>

---
title: "Pottery decor as networks on the Middle Niger"
author:
  - Nikolas Gestrich:
      email: gestrich@uni-frankfurt.de
      institute: [FI]
      correspondence: true
  - Juan-Marco Puerta-Schardt:
      email: Puerta-Schardt@em.uni-frankfurt.de
      institute: [GU]
      correspondence: false
institute:
  - FI: Frobenius Institute
  - GU: Goethe University
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      #pandoc_args:
      #- --lua-filter=../templates/scholarly-metadata.lua
      #- --lua-filter=../templates/author-info-blocks.lua
      #- --lua-filter=../templates/pagebreak.lua
      dpi: 300
abstract: |
  This paper reports on an attempt to analyse decorative techniques on archaeological pottery from the Middle Niger as knowledge exchange networks. The 12th-century CE state of this network is modelled and analysed, and then compared to its 9th-century counterpart. The analysis shows how knowledge about pottery decoration was propagated within networks of different sizes and intensities, from local, well-connected networks to more loosely tied long-distance connections. The article shows how the perspective of network analysis differs from, and can fruitfully complement, previous treatments of ceramic décor distribution in the region. It adds a novel perspective to what the distribution of archaeological ceramics in this region reflects, and contributes to the generation of hypotheses that can be further tested by fieldwork. 
keywords: |
  Mali; network analysis; pottery; archaeological ceramics

---

@@

## quality of data
```{r iNext overview, echo = FALSE}
library(iNEXT)

@@

```{r cluster3, fig.cap="Internal connections within community 3"}
decor_graph %>%
  activate(nodes) %>%
  mutate(deg = centrality_eigen(weights = weight)) %>%
  filter(louvain == 3) %>%
  ggraph(layout = "graphopt") +
  geom_edge_fan(aes(color = name, edge_width = weight, edge_alpha = weight)) +
  scale_edge_color_manual(values = decorcolor[E(decor_graph)$name]) +
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_point(aes(size = centrality_degree(weights = weight)), colour = "darkgreen") +
  geom_node_text(aes(label = label), col = "black", repel = TRUE) +
  theme_graph()
```

```{r cluster4, fig.cap="Internal connections within community 3"}
decor_graph %>%
  activate(nodes) %>%
  mutate(deg = centrality_eigen(weights = weight)) %>%
  filter(louvain == 4) %>%
  ggraph(layout = "graphopt") +
  geom_edge_fan(aes(color = name, edge_width = weight, edge_alpha = weight)) +
  scale_edge_color_manual(values = decorcolor[E(decor_graph)$name]) +
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_point(aes(size = centrality_degree(weights = weight)), colour = "yellow") +
  geom_node_text(aes(label = label), col = "black", repel = TRUE) +
  theme_graph()
```
